%
%
%
\section{NUMERICAL TESTS IN PARALLEL}

%
%
%
In this section we complement our theoretical estimates with the runtimes of a parallel implementation of our numerical system. 
We fix the size of the problem to 705600 volume points and vary the quantity and size of elements proportionally. 
Each hybridized system has more than 705600 points as the $\mathbf{F}$ and $\mathbf{F}^{\intercal}$ factors increase the size of the system as we add elements.
Our implementation was developed largely in PETSc and was tested on the Talapas cluster using an Intel Xeon E5-2690 v4 CPU.

\input{./figure/tts}
 
The most performant PDE solvers for large-scale problems are increasingly based on GPUs, but often do so by constraining properties of system, such as enforcing FPD-ness in the case of iterative solvers. We show that the hybrid SBP-SAT method can be compute similarly large problems with fewer constraints on the CPU.  

\subsection{Evaluation}
Three computational kernels comprise the majority of the runtime, SpMV via Eq. \eqref{}, MatMult via \eqref{}, and $\symbf{\lambda}$ linear solve via Eq. \eqref{}.

In our problem, the matrix-matrix solve in the global system takes a relatively small amount of time because we only have three unique matrices to solve. 
As we increase the number of elements, we decrease the size of these solves, resulting in it comprising an increasingly minimal portion of the overall runtime. 
In more heterogeneous systems this operation will consist of a marginally larger portion of the overall runtime.
Figure \ref{} the 



\input{./figure/runtime_components}


\subsection{MatMult Analysis}

\input{./figure/matmult_flopspers}

%\begin{mcfigure}
%	\centering
%	\input{./figure/total_gflops.tex}
%	\captionof{figure}{Total FLOPs used to compute the factorized matrix multiplication in $\textbf{F}^{\intercal} \times (\textbf{M}^{-1} \textbf{F})$ over the number of elements for a constant problem size, $N = 705\kern 0.25em 600$. FLOPs decrease as the size of the constituent inner products decrease in relation to the size of each element.}
%\end{mcfigure}

\subsection{SpMV Analysis}

\subsection{Delta Solve Analysis}

%\begin{mcfigure}
%	\centering
%	\input{./figure/serial_tts_trunc.tex}
%\end{mcfigure}

